Manuscript Figures for Genome Biology (simulation subset)

### 2018-08-30 manuscript_figures/manuscript_figures_sims.Rmd
Change subtitles in Figure 3

```{r}
genplot <- function(tab, cov, xt = "", met = c("FDR", "TPR"), ebw = 0.0025) {
    met <- match.arg(met)
    cov <- rlang::enquo(cov)
    gp <- dplyr::filter(tab, key == met) %>%
        ggplot(aes(x = !!cov, y = mean.info, color = Method, group = Method)) +
        geom_line(aes(linetype = Method), alpha = 0.85) +
        geom_errorbar(aes(ymin = mean.info - se.info, ymax = mean.info + se.info), width = ebw, alpha=0.5) +
        scale_linetype_manual(values = lty) + 
        scale_color_manual(values = col) +
        scale_y_continuous(met, labels = scales::percent) +
        expand_limits(y = 0) +
        ggtitle(paste("Mean", met)) +
        theme_classic() +
        theme(axis.title = element_text(face = "bold", size = 10),
              plot.title = element_text(face = "bold", size = 14))
    if (met == "FDR") {
        if (rlang::quo_name(cov) == "alpha") {
            gp <- gp + geom_abline(lty = 2, color = "blue", alpha = 1/2) 
        } else {
            gp <- gp + geom_hline(yintercept = 0.05, lty = 2, color = "blue", alpha = 1/2) 
        }
    }
    gp
}
```

@@

@@

@@

Fig3 <- plot_grid(p3a + guides(color = FALSE, linetype = FALSE),
                p3b + guides(color = FALSE, linetype = FALSE),
                p3c + guides(color = FALSE, linetype = FALSE),
                p3d + guides(color = FALSE, linetype = FALSE),
                p3e + guides(color = FALSE, linetype = FALSE),
                p3f + guides(color = FALSE, linetype = FALSE),
                labels = LETTERS[1:6], ncol = 2)
Fig3 <- plot_grid(Fig3, get_legend(p3a), rel_widths = c(1, .2))
Fig3
ggsave(file.path(outdir, "Figure3.pdf"), width=10, height=12)
```

@@

```{r, fig.width = 10, fig.height = 12}
## Figure 3plus A,B: FDR/TPR of methods across varying test statistics distribution
res_noise <- dplyr::filter(resmet, setting == "informative-cubic")
p3pa <- genplot(res_noise, cov = alpha, met = "FDR") +
    facet_grid(. ~ dist, labeller = label_parsed)
p3pb <- genplot(res_noise, cov = alpha, met = "TPR") +
    facet_grid(. ~ dist, labeller = label_parsed)

Fig3p <- plot_grid(p3pa + guides(color = FALSE, linetype = FALSE),
                   p3pb + guides(color = FALSE, linetype = FALSE),
                   labels = LETTERS[1:2], ncol = 1)
Fig3p <- plot_grid(Fig3p, get_legend(p3pa), rel_widths = c(7.5, 1))
Fig3p
ggsave(file.path(outdir, "Figure3plus.pdf"), width=14, height=8)
```

>>>>

```{r}
genplot <- function(tab, cov, xt = "", met = c("FDR", "TPR"), ebw = 0.0025) {
    met <- match.arg(met)
    cov <- rlang::enquo(cov)
    gp <- dplyr::filter(tab, key == met) %>%
        ggplot(aes(x = !!cov, y = mean.info, color = Method, group = Method)) +
        geom_line(aes(linetype = Method), alpha = 0.85) +
        geom_errorbar(aes(ymin = mean.info - se.info, ymax = mean.info + se.info), width = ebw, alpha=0.5) +
        scale_linetype_manual(values = lty) + 
        scale_color_manual(values = col) +
        scale_y_continuous(met, labels = scales::percent) +
        expand_limits(y = 0) +
        theme_classic() +
        theme(axis.title = element_text(face = "bold", size = 10),
              plot.title = element_text(face = "bold", size = 14))
    if (met == "FDR") {
        if (rlang::quo_name(cov) == "alpha") {
            gp <- gp + geom_abline(lty = 2, color = "blue", alpha = 1/2) 
        } else {
            gp <- gp + geom_hline(yintercept = 0.05, lty = 2, color = "blue", alpha = 1/2) 
        }
    }
    gp
}
```

@@

## add title to 3A,B
p3ab <- plot_grid(p3a + guides(color = FALSE, linetype = FALSE),
                  p3b + guides(color = FALSE, linetype = FALSE),
                  labels = LETTERS[1:2], ncol = 2)
p3abTitle <- ggdraw() +
    draw_label("Simulation performance across varying numbers of hypotheses",
               fontface = 'bold')
p3ab <- plot_grid(p3abTitle, p3ab, ncol = 1, rel_heights = c(0.1, 1))

@@

## add title to 3C,D
p3cd <- plot_grid(p3c + guides(color = FALSE, linetype = FALSE),
                  p3d + guides(color = FALSE, linetype = FALSE),
                  labels = LETTERS[3:4], ncol = 2)
p3cdTitle <- ggdraw() +
    draw_label("Simulation performance across varying null proportion",
               fontface = 'bold')
p3cd <- plot_grid(p3cdTitle, p3cd, ncol = 1, rel_heights = c(0.1, 1))

@@

## add title to 3E,F
p3ef <- plot_grid(p3e + guides(color = FALSE, linetype = FALSE),
                  p3f + guides(color = FALSE, linetype = FALSE),
                  labels = LETTERS[5:6], ncol = 2)
p3efTitle <- ggdraw() +
    draw_label("Simulation performance across varying informativeness",
               fontface = 'bold')
p3ef <- plot_grid(p3efTitle, p3ef, ncol = 1, rel_heights = c(0.1, 1))

## pull Figure 3 together
Fig3 <- plot_grid(p3ab, p3cd, p3ef, ncol = 1)
Fig3 <- plot_grid(Fig3, get_legend(p3a), rel_widths = c(1, .2))
Fig3
ggsave(file.path(outdir, "Figure3.pdf"), width=10, height=12)
```

@@

```{r, fig.width = 10, fig.height = 12}
## Figure 3plus A,B: FDR/TPR of methods across varying test statistics distribution
res_noise <- dplyr::filter(resmet, setting == "informative-cubic")
levels(res_noise$dist) <- gsub("Noise:", "Distribution:", levels(res_noise$dist))
p3pa <- genplot(res_noise, cov = alpha, met = "FDR") +
    facet_grid(. ~ dist, labeller = label_parsed)
p3pb <- genplot(res_noise, cov = alpha, met = "TPR") +
    facet_grid(. ~ dist, labeller = label_parsed)

## create title for 3plus
p3pTitle <- ggdraw() +
    draw_label("Simulation performance across test statistic distributions",
               fontface = 'bold', size = 20)

## pull Figure 3plus together
Fig3p <- plot_grid(p3pa + guides(color = FALSE, linetype = FALSE),
                   p3pb + guides(color = FALSE, linetype = FALSE),
                   labels = LETTERS[1:2], ncol = 1)
Fig3p <- plot_grid(p3pTitle, Fig3p, ncol = 1, rel_heights = c(0.1, 1))
Fig3p <- plot_grid(Fig3p, get_legend(p3pa), rel_widths = c(7.5, 1))
Fig3p
ggsave(file.path(outdir, "Figure3plus.pdf"), width=14, height=8)
```
